Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-07 paper/paper1/ms.tex
Some uncommited changes to the paper text

\documentclass[modern]{aastex631}
\bibliographystyle{aasjournal}

@@

A total of \censor{xx} systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.

We specified our observations on the HAT-P-67 system due to its unique rotational period. HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b. An extremely low density object, HAT-P-67b loses its atmosphere rather rapidly for transiting an evolved host star.

@@

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-schedule 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from 8100-12800 \AA spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censor{xx} other nights.

\authorcomment1{We may want to put a observation log here, grouped by night.}
% \input{tables/observation_flat_table.tex}

>>>>

\documentclass[twocolumn]{aastex631}
\bibliographystyle{aasjournal}

@@

At least 8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.

Here we present a study of the exosphere of HAT-P-67b.  HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b.  HAT-P-67b stands out for a few reasons.  It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss, all else being equal.  It orbits an evolved star, which means it could have changed its instellation recently as the star's size and radiaiton properties have changed.  The star appears close to the star, making it conceivable that star-planet interactions could be at play.  These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.

@@

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\mathrm{\AA}\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censorbox{xx} other nights.

\input{tables/observations_flat_table.tex}
